dyngen: a multi-modal simulator for spearheading new single-cell omics analyses

### 2021-05-17 manuscript/manuscript.Rmd
update for v5
update

---
title: "dyngen: a multi-modal simulator for spearheading new single-cell omics analyses"
author:
- name: Robrecht Cannoodt
  institute: [dambi, twist, di]
  equal_contributor: true
- name: Wouter Saelens
  institute: [dambi, twist, epfl]
  equal_contributor: true
- name: Louise Deconinck
  institute: [dambi, twist]
- name: Yvan Saeys
  institute: [dambi, twist]
  correspondence: true
  email: yvan.saeys@ugent.be
institute: 
  - dambi: Data Mining and Modelling for Biomedicine group, VIB Center for Inflammation Research, Ghent, Belgium
  - twist: Department of Applied Mathematics, Computer Science, and Statistics, Ghent University, Ghent, Belgium
  - di: Data Intuitive, Lebbeke, Belgium
  - epfl: Institute of Bioengineering, School of Life Sciences, École Polytechnique Fédérale de Lausanne (EPFL), Lausanne, Switzerland
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    keep_tex: yes
    latex_engine: xelatex
    citation_package: biblatex
    pandoc_args:
      - '--lua-filter=lua/scholarly-metadata.lua'
      - '--lua-filter=lua/author-info-blocks.lua'
biblatexoptions: sorting=none,url=false,backend=bibtex
classoption:
- table
- 10pt
- a4paper
header-includes: |
  \usepackage{tcolorbox}
  \usepackage{colortbl}
  \usepackage{booktabs}
  \usepackage{tabularx}
  \usepackage{fontspec}
  \usepackage{pifont}
  \usepackage{float}
  \usepackage{caption}
  \captionsetup[table]{position=bottom}
  \setmainfont [Path = fonts/,
    UprightFont = *-300,
    ItalicFont = *-300-Italic,
    BoldFont = *-700,
    BoldItalicFont = *-700-Italic
  ]{MuseoSans}

@@

\begin{eqnarray*}
  \text{regeffect}_G & = \frac{\text{proptrans}_G(S) - \text{proptrans}_G(S[\z T \leftarrow 0])}{\xpr G}
\end{eqnarray*}

@@

>>>>

---
title: "dyngen: a multi-modal simulator for spearheading new single-cell omics analyses"
author:
- name: Robrecht Cannoodt
  institute: [dambi, twist, di]
  equal_contributor: true
- name: Wouter Saelens
  institute: [dambi, twist, epfl]
  equal_contributor: true
- name: Louise Deconinck
  institute: [dambi, twist]
- name: Yvan Saeys
  institute: [dambi, twist]
  correspondence: true
  email: yvan.saeys@ugent.be
institute: 
  - dambi: Data Mining and Modelling for Biomedicine group, VIB Center for Inflammation Research, Ghent, Belgium
  - twist: Department of Applied Mathematics, Computer Science, and Statistics, Ghent University, Ghent, Belgium
  - di: Data Intuitive, Lebbeke, Belgium
  - epfl: Institute of Bioengineering, School of Life Sciences, École Polytechnique Fédérale de Lausanne (EPFL), Lausanne, Switzerland
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    keep_tex: yes
    latex_engine: xelatex
    citation_package: biblatex
    pandoc_args:
      - '--lua-filter=lua/scholarly-metadata.lua'
      - '--lua-filter=lua/author-info-blocks.lua'
biblatexoptions: sorting=none,url=false
classoption:
- table
- 10pt
- a4paper
header-includes: |
  \usepackage{tcolorbox}
  \usepackage{colortbl}
  \usepackage{booktabs}
  \usepackage{tabularx}
  \usepackage{fontspec}
  \usepackage{pifont}
  \usepackage{float}
  \usepackage{caption}
  \captionsetup[table]{position=bottom}

@@

\begin{eqnarray}
  \text{regeffect}_G & = \frac{\text{proptrans}_G(S) - \text{proptrans}_G(S[\z T \leftarrow 0])}{\xpr G}
\end{eqnarray}

@@

# Acknowledgements
This project has been made possible in part by grant number 2020-218899 from the Chan Zuckerberg
Initiative DAF, an advised fund of Silicon Valley Community Foundation.
